%Two resources useful for abstract writing.
% Guidance of how to write an abstract/summary provided by Nature: https://cbs.umn.edu/sites/cbs.umn.edu/files/public/downloads/Annotated_Nature_abstract.pdf %https://writingcenter.gmu.edu/guides/writing-an-abstract
\chapter*{\center \Large  Abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Replace all text with your text
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In order to enchance MNIST classification this research conducts an in-depth 
comparative analysis between two powerful architectures: the Denoising Autoencoder (DAE) and 
the Convolutional Neural Network (CNN). Both models are well-regarded for their distinct 
capabilities — DAE excels in unsupervised learning and feature extraction, while CNN is 
tailored for image-based tasks, particularly  classification. The purpose of this study is to enhance the performance of MNIST digit classification, this study navigates through the 
architectures of DAE and CNN, analyzing their impact on classification accuracy and noise 
resilience. The research extends beyond traditional performance metrics, delving into the 
interpretability of learned representations and assessing the models' ability to handle noisy 
input data. The research problem centers on deciphering how these architectures influence MNIST 
classification under varying levels of noise, providing insights into their respective 
strengths and limitations.  By addressing this research problem, the study aims to contribute 
to the advancement of image classification techniques, offering nuanced guidance on selecting 
models for MNIST classification tasks, especially in scenarios with noisy input data. The 
significance of this research lies in its potential to improve the resilience of classification 
models to real-world noise, thereby enhancing their applicability in practical settings. The 
findings are expected to benefit practitioners and researchers alike, guiding them in the 
selection and optimization of models for noise-affected MNIST classification scenarios.


~\\[1cm]
\noindent % Provide your key words
\textbf{Keywords:} Deep Learning, Denoising Autoencoder,
Convolutional Neural Networks, Classification, Accuracy.